### 2016-03-15 paper/result_optical_flow.tex
Hang

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \end{subfigure}
  \caption{Energy plots per thread. Left: Parallel Fusion  
    Move (PFM). Right: SF-MF(ours).}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
\end{subfigure}
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
\end{subfigure}
\caption{Energy
  plots for optical flow under difference configurations. Left:
  varying $\beta$; right: varying solution sharing
  frequencies. Solution sharing achieves better convergence, but
  sharing too many solutions (larger $\beta$) or sharing solutions too
  frequently (less $k$) slows down the convergence, as it reduces the
  time for exploration.}
  \label{opticalflow_configuration}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \end{subfigure}
  \caption{Energy plots per thread. Left: Parallel Fusion  
    Move (PFM). Right: SF-MF(ours).}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
\end{subfigure}
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
\end{subfigure}
\caption{Energy
  plots for optical flow under difference configurations. Left:
  varying $\beta$; right: varying solution sharing
  frequencies. Solution sharing achieves better convergence, but
  sharing too many solutions (larger $\beta$) or sharing solutions too
  frequently (less $k$) slows down the convergence, as it reduces the
  time for exploration.} \label{fig:opticalflow_configuration}
\end{figure}

### 2016-03-15 paper/stereo.tex
Hang

\noindent For simple stereo problems with submodular energy as ours, the
sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly
informative, where efficient inference algorithms such as graph-cuts
exist.
%Our experiments have also supported this, where the fusion method
%(i.e., the use of proposal generation) rather makes it slow due to the
%overhead, while not improving final energy.
Therefore, we have chosen algorithms based on Alpha-Expansion, namely
single thread Alpha Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion} to
be competing methods. For HF, we use Alpha-Expansion at the leaf node of
the label tree or QPBO in the other cases.
%when either of the
%child node is leaf node (constant label) and QPBO for all other nodes.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
solution sharing), and the standard SF.
%
SF-MF implies $\alpha+\beta=1$, where each thread repeats
fusing a solution proposal ($\alpha=1, \beta=0$) for four iterations
by Graph-cuts and fusing a concurrent solution  ($\alpha=0, \beta=1$)
for one iteration by QPBO.
%expand 4 labels (repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha
%Expansion and then fuse one solution from other threads ($\alpha=0,
%\beta=1$) by QPBO.
In the later case, a thread randomly chooses one solution from the
solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is the
free parameter and set to 4. In this case one thread will fuse 4 labels,
together with current solution by TRW-S per iteration and never
exchanges solutions with other threads. We perform a multi-way fusion
of solutions from all the threads at the end to obtain a final solution
% at
% the end to fuse solutions from all the threads to a single solution
(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our solution proposals
to be constant-label proposals.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\noindent For simple stereo problems with submodular energy as ours, the
sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly
informative, where efficient inference algorithms such as graph-cuts
exist.
%Our experiments have also supported this, where the fusion method
%(i.e., the use of proposal generation) rather makes it slow due to the
%overhead, while not improving final energy.
Therefore, we have chosen algorithms based on Alpha-Expansion, namely
single thread Alpha Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion} to
be competing methods. For HF, we use Alpha-Expansion at the leaf node of
the label tree and QPBO in the other cases.
%when either of the
%child node is leaf node (constant label) and QPBO for all other nodes.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
solution sharing), and the standard SF.
%
SF-MF implies $\alpha+\beta=1$, where each thread repeats
fusing a solution proposal ($\alpha=1, \beta=0$) for four iterations
by Graph-cuts and fusing a concurrent solution  ($\alpha=0, \beta=1$)
for one iteration by QPBO.
%expand 4 labels (repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha
%Expansion and then fuse one solution from other threads ($\alpha=0,
%\beta=1$) by QPBO.
In the later case, a thread randomly chooses one solution from the
solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is
the free parameter and set to 4. In this case one thread will fuse 4
labels, together with current solution in that thread by TRW-S in each
iteration and never exchanges solutions with other threads. We perform
a multi-way fusion of solutions from all the threads at the end to
obtain a final solution
% at
% the end to fuse solutions from all the threads to a single solution
(similar to PAE). For standard SF architecture, we have used
($\alpha=4, \beta=1$).  To make the comparison simple, we restrict our
solution proposals to be constant-label proposals.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
